\makeatletter
\def\input@path{{../}}
\makeatother
\documentclass[../Thesis.tex]{subfiles}
\begin{document}
\chapter{Introduction}
\section{Background}
Gas phase calculations for Quantum chemical systems have well defined and
reliable results which can be used to predict properties from several systems in vacuum.
Although, it is rare for an experimental chemist to work with gas phase properties.
Most of the processes of interest chemical pricesses and mechanisms happen while in a solvent \cite{FossoTande:2013ka}.
Therefore it is important to be able to produce reliable results when working
with these systems. Many models exist to solve this system, outlined in chapter
\ref{chap:Solvent_effect}, but, in this thesis, we will mainly focusing on \ac{PCM}.

A big hurdle for \ac{PCM} is working with the sharp transition between solvent and
solute. Numerous methods have been implemented in order to minimize the discontinuity
at this boundary \cite{Tomasi:2005ipa}. Our approach is to define both the solvent
and substrate environments as an analytical function represented with \ac{MW} basis.

\ac{MW} are a part of a family of basis classified under \ac{MRA}. \ac{MW} basis
sets have useful characteristics for development of solutions of partial differential equations.
These are orthogonality of wavelet spaces, vanishing moments and locally adaptive
representations of functions, which allow for further refining critical areas of a system.

\section{Summary of results}
The main goal with this project was to have a working implementation of solvent
effect in \ac{MW} basis by following in Fosso--tande's footsteps \cite{FossoTande:2013ka}.
Another objective was to implement a variational formulation of the \ac{GPE}
as defined in \cite{Lipparini:2010bg}.

We found that the implementation managed to produce values that did not differ
significantly from exact calculations of the properties tested, these being the Born energy of
the solvent \cite{Tomasi:1994wt} and Gauss' theorem as defined in \cite{Sorland}.
The energy calculations yielded results that converged towards Gaussian results
as the radii increased. We also tested the Variational formulation of the
\ac{GPE} shown in \cite{Lipparini:2010bg}, which gave promising results for
small systems, such as \ce{Li^+}, but showed room for improvement for bigger systems.



\section{Structure of the thesis}
In chapter \ref{chap:Quantum_chemistry} of this thesis the quantum
and computational Chemical formalism will be presented along with  methods used
to solve systems. Among these are the Born--Oppenheimer approximation, variational principle, \ac{HF} method and
\ac{DFT}.

Some examples of Wavelet basis are shown and Chapter \ref{chap:MW_basis} will mention some basis sets and define \ac{MW}
the implementation of different operators is described.

Chapter \ref{chap:Solvent_effect}
describes the particular system we work with in this thesis, namely, solvent
effect and the reaction potential. This chapter will also introduce a new variational
formulation of the \ac{GPE} used in solving the electrostatic reaction field problem.

Chapter \ref{chap:implementation} describes how the reaction field Potential was implemented
using \mrchem. It will also describe the way the variational formulation was implemented.

Chapter \ref{chap:Results} Goes through the systems that were used to test the implementation,
along with the type of tests that were performed. The results will be tabulated and
some figures will be shown. Finally an analysis and discussion of the results will be
presented along with points of improvement and future development.
\section{Notation}
Notation differs slightly between works in computational and Quantum Chemistry.
Most of the equations and formulas use the same standard notation, while others
might differ slightly in accents and other details in their notations. Therefore
in this section a summarization of notation used in this thesis will be given.

The following Table \ref{tab:notation} shows most of the notation used for
common objects in mathematics and quantum mechanics.

\begin{table}[h!]
    \resizebox{\textwidth}{!}{
  \begin{tabular}{|l|l|c|}
    \hline
    Object & Description of notation & Examples\\  \hline
    \rule{0pt}{12.5pt}vectors & lower case letter, or symbol, with an arrow above them & $\rvec, \vec{x}, \vec{\Psi}$ \\  \hline
    \rule{0pt}{12.5pt}vector elements & lower case letter, or symbol, with an arrow above them and index subscripts &  $\rvec_i, \vec{x}_1, \vec{\Psi}_x$ \\ \hline
    \rule{0pt}{12.5pt}matrices & Upper case letter or symbols with a line above them &  $\bar{A}, \bar{F}, \bar{S}$ \\ \hline
    \rule{0pt}{12.5pt}matrix elements &   Upper case letter  with a line above them and index subscripts (rows, columns) &  $\bar{A}_{ij}, \bar{F}_{11}, \bar{S}_{\mu\nu}$\\  \hline
    \rule{0pt}{12.5pt}Operators & Presented as a symbol with a \^~above it & $\hat{O}, \hat{H}, \hat{F}$  \\  \hline
    \rule{0pt}{12.5pt}functions & presented by a letter with their input variables enclosed in parentheses () & $f(x), \Psi(\rvec)$\\  \hline
    \rule{0pt}{12.5pt}functionals & presented by a letter with their input functions enclosed in square brackets [] & $E[f], F[\Psi]  $\\  \hline
  \end{tabular}}{\caption{Notation used in this thesis}\label{tab:notation}}
\end{table}

Because we are working with atomic units, many of the common constants are reduced
to unit value. The constants used in this thesis are the elementary charge $e$
the reduced Planck constant $\hbar$, the electron mass $m_e$ and
vacuum permittivity $\epso$ are all unit value.

Finally, we will be working in Dirac notation, which means we write a state
vector of a wave function $\Psi$ as $\ket{\Psi}$ and its
complex conjugate as $\bra{\Psi}$. The scalar product in Dirac notation is
defined as
\begin{equation}\label{eq:diracproduc}
  \braket{\Psi|\Phi} = \int_{\Real^3} \Psi^{\star}\Phi \text{d}\rvec
\end{equation}
\input{acronyms.tex}
\biblio
\end{document}
